---
title: "02data_analysis"
author: "Spiro Stilianoudakis"
date: "February 8, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages

```{r}
library(MVN)
library(ggplot2)
library(car)
#library(lsmeans)
library(ggpubr)
#library(ICSNP)
library(knitr)
library(dplyr)
library(tidyverse)  
library(gridExtra)
library(psych)
library(MASS)
#library(pca3d)
#library(factoextra)
#library(CCA)
#library(CCP)
library(GGally)
#library(GPArotation)
library(corrplot)
library(lsmeans)
library(psych)
library(reshape)
library(reshape2)
library(irr)
```

# Setting Working Directory

```{r}
setwd("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Susie")
```

# Reading in Data

```{r}
big5data_final <- readRDS("big5data_final.rds")

big5data_final$Ethnicity[which(big5data_final$Ethnicity=="Black/African American" |
                                 big5data_final$Ethnicity=="Hispanic")] <- "Other"

persondat <- readRDS("persondat.rds")
questdat <- readRDS("questdat.rds")

#rename openness to experience as just openness
names(big5data_final)[15] <- "Openness"

#check missing scores
big5data_final[!complete.cases(big5data_final[,11:15]),11:15]

#Use mean imputation to fill in miss scores
#big5data_final[16,12] <- mean(big5data_final$Agreeableness[which(big5data_final$Gender=="Male")], na.rm=TRUE)
big5data_final[16,12] <- mean(big5data_final$Agreeableness, na.rm=TRUE)

#big5data_final[40,11] <- mean(big5data_final$Extraversion[which(big5data_final$Gender=="Female")], na.rm=TRUE)
big5data_final[40,11] <- mean(big5data_final$Extraversion, na.rm=TRUE)

#big5data_final[40,13] <- mean(big5data_final$Conscientiousness[which(big5data_final$Gender=="Female")], na.rm=TRUE)
big5data_final[40,13] <- mean(big5data_final$Conscientiousness, na.rm=TRUE)

#big5data_final[40,15] <- mean(big5data_final$Openness[which(big5data_final$Gender=="Female")], na.rm=TRUE)
big5data_final[40,15] <- mean(big5data_final$Openness, na.rm=TRUE)

#sanity check
big5data_final[!complete.cases(big5data_final[,11:15]),11:15]

#mean imputation for missing values for schools accepted to
big5data_final$Schools.accepted.to[is.na(big5data_final$Schools.accepted.to)] <- mean(big5data_final$Schools.accepted.to, na.rm=TRUE)

```

# Demographics Table

## Total
```{r}
#year
table(big5data_final$Year)
prop.table(table(big5data_final$Year))

#age
table(big5data_final$Age)
prop.table(table(big5data_final$Age))

#gender
table(big5data_final$Gender)
prop.table(table(big5data_final$Gender))

#ethnicity
table(big5data_final$Ethnicity)
prop.table(table(big5data_final$Ethnicity))

#residency
table(big5data_final$Residency)
prop.table(table(big5data_final$Residency))

#schools applied to
mean(big5data_final$Schools.applied.to)
sd(big5data_final$Schools.applied.to)

#schools accepted to
#mean(big5data_final$Schools.accepted.to)
#sd(big5data_final$Schools.accepted.to)

#undergrad gpa
mean(big5data_final$Undergrad.GPA)
sd(big5data_final$Undergrad.GPA)

#dat score
mean(big5data_final$DAT.score)
sd(big5data_final$DAT.score)


```

##Stratified by Personality

```{r}
#year
table(big5data_final$Year, big5data_final$Personality)
round(prop.table(table(big5data_final$Year, big5data_final$Personality), 1),2)

#age
table(big5data_final$Age, big5data_final$Personality)
round(prop.table(table(big5data_final$Age, big5data_final$Personality), 1),2)

#gender
table(big5data_final$Gender, big5data_final$Personality)
round(prop.table(table(big5data_final$Gender, big5data_final$Personality), 1),2)


#ethnicity
table(big5data_final$Ethnicity, big5data_final$Personality)
round(prop.table(table(big5data_final$Ethnicity, big5data_final$Personality), 1),2)


#residency
table(big5data_final$Residency, big5data_final$Personality)
round(prop.table(table(big5data_final$Residency, big5data_final$Personality), 1),2)


#schools applied to 
tapply(big5data_final$Schools.applied.to, big5data_final$Personality, mean)
tapply(big5data_final$Schools.applied.to, big5data_final$Personality, sd)


#undergrad gpa
tapply(big5data_final$Undergrad.GPA, big5data_final$Personality, mean)
tapply(big5data_final$Undergrad.GPA, big5data_final$Personality, sd)


#dat score
tapply(big5data_final$DAT.score, big5data_final$Personality, mean)
tapply(big5data_final$DAT.score, big5data_final$Personality, sd)



```

##Significance tests

```{r}
#year
fisher.test(table(big5data_final$Year, big5data_final$Personality))

#age
fisher.test(table(big5data_final$Age, big5data_final$Personality))

#gender
fisher.test(table(big5data_final$Gender, big5data_final$Personality))

#ethnicity
fisher.test(table(big5data_final$Ethnicity, big5data_final$Personality))

#residency
fisher.test(table(big5data_final$Residency, big5data_final$Personality))

#schools applied to
summary(aov(Schools.applied.to ~ Personality, data=big5data_final))

#undergrad gpa
summary(aov(Undergrad.GPA ~ Personality, data=big5data_final))

#dat score
summary(aov(DAT.score ~ Personality, data=big5data_final))

```

# MANOVA (revised 3/15/19)

```{r}

model <- lm(cbind(Extraversion, 
                  Agreeableness,
                  Conscientiousness, 
                  Neuroticism, 
                  Openness) ~ Gender + Year +  Age + Undergrad.GPA + DAT.score + Residency + Ethnicity, data=big5data_final)

summary(manova(model), test = "Wilks")
summary(manova(model), test = "Roy")

#lsm <- lsmeans(model, "Gender")
#test(contrast(lsm, "pairwise"), side = "=",  adjust = "tukey")

#Agreeableness
mean(big5data_final$Agreeableness[which(big5data_final$Gender=="Male")])
mean(big5data_final$Agreeableness[which(big5data_final$Gender=="Female")])
sd(big5data_final$Agreeableness[which(big5data_final$Gender=="Male")])
sd(big5data_final$Agreeableness[which(big5data_final$Gender=="Female")])

tapply(big5data_final$Agreeableness, big5data_final$Year, mean)
tapply(big5data_final$Agreeableness, big5data_final$Year, sd)

#Conscientiousness
mean(big5data_final$Conscientiousness[which(big5data_final$Gender=="Male")])
mean(big5data_final$Conscientiousness[which(big5data_final$Gender=="Female")])
sd(big5data_final$Conscientiousness[which(big5data_final$Gender=="Male")])
sd(big5data_final$Conscientiousness[which(big5data_final$Gender=="Female")])

tapply(big5data_final$Conscientiousness, big5data_final$Year, mean)
tapply(big5data_final$Conscientiousness, big5data_final$Year, sd)

#Neuroticism
mean(big5data_final$Neuroticism[which(big5data_final$Gender=="Male")])
mean(big5data_final$Neuroticism[which(big5data_final$Gender=="Female")])
sd(big5data_final$Neuroticism[which(big5data_final$Gender=="Male")])
sd(big5data_final$Neuroticism[which(big5data_final$Gender=="Female")])

tapply(big5data_final$Neuroticism, big5data_final$Year, mean)
tapply(big5data_final$Neuroticism, big5data_final$Year, sd)

#Extraversion
mean(big5data_final$Extraversion[which(big5data_final$Gender=="Male")])
mean(big5data_final$Extraversion[which(big5data_final$Gender=="Female")])
sd(big5data_final$Extraversion[which(big5data_final$Gender=="Male")])
sd(big5data_final$Extraversion[which(big5data_final$Gender=="Female")])

tapply(big5data_final$Extraversion, big5data_final$Year, mean)
tapply(big5data_final$Extraversion, big5data_final$Year, sd)

#Openness
mean(big5data_final$Openness[which(big5data_final$Gender=="Male")])
mean(big5data_final$Openness[which(big5data_final$Gender=="Female")])
sd(big5data_final$Openness[which(big5data_final$Gender=="Male")])
sd(big5data_final$Openness[which(big5data_final$Gender=="Female")])

tapply(big5data_final$Openness, big5data_final$Year, mean)
tapply(big5data_final$Openness, big5data_final$Year, sd)


summary.aov(lm(cbind(Extraversion, 
                  Agreeableness,
                  Conscientiousness, 
                  Neuroticism, 
                  Openness) ~ Gender + Year, data=big5data_final))

model2 <- lm(cbind(Extraversion, 
                  Agreeableness,
                  Conscientiousness, 
                  Neuroticism, 
                  Openness) ~ Gender + Year, data=big5data_final)

#adjusted
##gender
p.adjust(c(summary.aov(model2)$` Response Agreeableness`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Conscientiousness`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Neuroticism`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Extraversion`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Openness`$`Pr(>F)`[1]),
              method = "bonferroni")
##year
p.adjust(c(summary.aov(model2)$` Response Agreeableness`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Conscientiousness`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Neuroticism`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Extraversion`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Openness`$`Pr(>F)`[2]),
              method = "bonferroni")

#unadjusted
##gender
round(c(summary.aov(model2)$` Response Agreeableness`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Conscientiousness`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Neuroticism`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Extraversion`$`Pr(>F)`[1],
              summary.aov(model2)$` Response Openness`$`Pr(>F)`[1]),4)
##year
round(c(summary.aov(model2)$` Response Agreeableness`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Conscientiousness`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Neuroticism`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Extraversion`$`Pr(>F)`[2],
              summary.aov(model2)$` Response Openness`$`Pr(>F)`[2]),4)

```

#Investigating Agreeableness

```{r}
agreedat <- questdat[,c(1,3,8,13,18, 23,28,33,38,43,48)]

#recoding word responses to numeric responses
##omit first column (ID) and 6th column (already numeric)
agreedat[,-c(1,6)] <- apply(agreedat[,-c(1,6)], 2, function(x){ifelse(x=="Very Accurate", 5, 
                                           ifelse(x=="Moderately Accurate", 4,
                                                  ifelse(x=="Neither Accurate nor Inaccurate", 3, 
                                                         ifelse(x=="Moderately Inaccurate", 2,
                                                               ifelse(x=="Very Inaccurate", 1, NA)))))})

#reverse code negative questions
agreedat[,c(2,4,6,8)] <- apply(agreedat[,c(2,4,6,8)], 2, function(x){ifelse(x==1, 5, 
                                           ifelse(x==2, 4,
                                                  ifelse(x==3, 3, 
                                                         ifelse(x==4, 2,
                                                               ifelse(x==5, 1, NA)))))})

agreedat <- agreedat[which(agreedat$Record.ID %in% big5data_final$Id),]

agreedat$Gender <- big5data_final$Gender[which(big5data_final$Id %in% agreedat$Record.ID)]

malecor <- cor(agreedat[which(agreedat$Gender=="Male"),-c(1,12)], method = "spearman")
femalecor <- cor(agreedat[which(agreedat$Gender=="Female"),-c(1,12)], method = "spearman")


model2 <- lm(cbind(Feel.little.concern.for.others., 
                  Am.interested.in.people.,
                  Insult.people., 
                  Sympathize.with.others..feelings., 
                  Am.not.interested.in.other.people.s.problems.,
                  Have.a.soft.heart.,
                  Am.not.really.interested.in.others.,
                  Take.time.out.for.others.,
                  Feel.others..emotions.,
                  Make.people.feel.at.ease.) ~ Gender, data=agreedat)

summary(manova(model2))

summary.aov(model2)

round(p.adjust(c(summary.aov(model2)$` Response Feel.little.concern.for.others.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Am.interested.in.people.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Insult.people.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Sympathize.with.others..feelings.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Am.not.interested.in.other.people.s.problems.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Have.a.soft.heart.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Am.not.really.interested.in.others.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Take.time.out.for.others.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Feel.others..emotions.`$`Pr(>F)`[1],
summary.aov(model2)$` Response Make.people.feel.at.ease.`$`Pr(>F)`[1]),
method = "bonferroni"),4)

#nonparametric
##adjusted
round(p.adjust(c(kruskal.test(Feel.little.concern.for.others. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Am.interested.in.people. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Insult.people. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Sympathize.with.others..feelings. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Am.not.interested.in.other.people.s.problems. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Have.a.soft.heart. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Am.not.really.interested.in.others. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Take.time.out.for.others. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Feel.others..emotions. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Make.people.feel.at.ease. ~ as.factor(Gender), data = agreedat)$p.value), 
method="bonferroni"), 4)

##unadjusted
round(c(kruskal.test(Feel.little.concern.for.others. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Am.interested.in.people. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Insult.people. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Sympathize.with.others..feelings. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Am.not.interested.in.other.people.s.problems. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Have.a.soft.heart. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Am.not.really.interested.in.others. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Take.time.out.for.others. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Feel.others..emotions. ~ as.factor(Gender), data = agreedat)$p.value,
kruskal.test(Make.people.feel.at.ease. ~ as.factor(Gender), data = agreedat)$p.value), 4)


#plots
#agreedatplot <- melt(agreedat[,-1])

#ggplot(agreedatplot, aes(x=variable, y=value, fill=Gender)) +
#  #stat_boxplot(geom = "errorbar")+
#  geom_boxplot(position=position_dodge(1))+
#  geom_boxplot(aes(fill = Evaluation))

lapply(agreedat[,-c(1,12)],function(x){
       tapply(x, agreedat$Gender, median)})
lapply(agreedat[,-c(1,12)],function(x){
       tapply(x, agreedat$Gender, summary)})
```

##kappa

```{r}
agreedat2 <- agreedat[,-c(1,12)]

M <- cor(agreedat2, method = "spearman")
#corrplot(M, type="upper")

kappamat <- matrix(nrow = dim(agreedat2)[2],
                   ncol = dim(agreedat2)[2])

for(i in 1:dim(agreedat2)[2]){
  for(j in 1:dim(agreedat2)[2]){
    kappamat[i,j] <- kappa2(agreedat2[,c(i,j)], weight = "squared")$value
  }
}

colnames(kappamat) <- rownames(kappamat) <- c("Feel little concern for others",
                                              "Am interested in people",
                                              "Insult people",
                                              "Sympathize with others' feelings",
                                              "Am not interested in other peoples' problems",
                                              "Have a soft heart",
                                              "Am not really interested in others",
                                              "Take time out for others",
                                              "Feel others' emotions",
                                              "Make people feel at ease")

pmat <- matrix(nrow = dim(agreedat2)[2],
                   ncol = dim(agreedat2)[2])

for(i in 1:dim(agreedat2)[2]){
  for(j in 1:dim(agreedat2)[2]){
    pmat[i,j] <- kappa2(agreedat2[,c(i,j)], weight = "squared")$p.value
  }
}

diag(pmat) <- 0

col <- colorRampPalette(rev(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA")))
corrplot(kappamat, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=90, #Text label color and rotation
         # Combine with significance
         #p.mat = pmat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE, 
         cl.pos = "n",
         tl.cex = .75,
         number.cex = .75
)
```

##Cronbachs alpha

```{r}
agree.alpha <- psych::alpha(agreedat2, n.iter = 10000)
```


#Investigating Emotional stability

```{r}
emotdat <- questdat[,c(1,5,10,15,20,25,30,35,40,45,50)]

#recoding word responses to numeric responses
emotdat[,-1] <- apply(emotdat[,-1], 2, function(x){ifelse(x=="Very Accurate", 5, 
                                           ifelse(x=="Moderately Accurate", 4,
                                                  ifelse(x=="Neither Accurate nor Inaccurate", 3, 
                                                         ifelse(x=="Moderately Inaccurate", 2,
                                                               ifelse(x=="Very Inaccurate", 1, NA)))))})

#reverse code negative questions
emotdat[,c(2,4,6,7,8,9,10,11)] <- apply(emotdat[,c(2,4,6,7,8,9,10,11)], 2, function(x){ifelse(x==1, 5, 
                                           ifelse(x==2, 4,
                                                  ifelse(x==3, 3, 
                                                         ifelse(x==4, 2,
                                                               ifelse(x==5, 1, NA)))))})

emotdat <- emotdat[which(emotdat$Record.ID %in% big5data_final$Id),]

emotdat$Gender <- big5data_final$Gender[which(big5data_final$Id %in% emotdat$Record.ID)]

malecor <- cor(emotdat[which(emotdat$Gender=="Male"),-c(1,12)], method = "spearman")
femalecor <- cor(emotdat[which(emotdat$Gender=="Female"),-c(1,12)], method = "spearman")

#nonparametric
##adjusted
round(p.adjust(c(kruskal.test(Get.stressed.out.easily. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Am.relaxed.most.of.the.time. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Worry.about.things. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Seldom.feel.blue. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Am.easily.disturbed. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Get.upset.easily. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Change.my.mood.a.lot. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Have.frequent.mood.swings. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Get.irritated.easily. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Often.feel.blue. ~ as.factor(Gender), data = emotdat)$p.value),
method = "bonferroni"), 4)

##unadjusted
round(c(kruskal.test(Get.stressed.out.easily. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Am.relaxed.most.of.the.time. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Worry.about.things. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Seldom.feel.blue. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Am.easily.disturbed. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Get.upset.easily. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Change.my.mood.a.lot. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Have.frequent.mood.swings. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Get.irritated.easily. ~ as.factor(Gender), data = emotdat)$p.value,
kruskal.test(Often.feel.blue. ~ as.factor(Gender), data = emotdat)$p.value), 4)


lapply(emotdat[,-c(1,12)],function(x){
       tapply(x, emotdat$Gender, median)})
lapply(emotdat[,-c(1,12)],function(x){
       tapply(x, emotdat$Gender, summary)})
```

##kappa

```{r}
emotdat2 <- emotdat[,-c(1,12)]

M <- cor(emotdat2, method = "spearman")
#corrplot(M, type="upper")

kappamat <- matrix(nrow = dim(emotdat2)[2],
                   ncol = dim(emotdat2)[2])

for(i in 1:dim(emotdat2)[2]){
  for(j in 1:dim(emotdat2)[2]){
    kappamat[i,j] <- kappa2(emotdat2[,c(i,j)], weight = "squared")$value
  }
}

colnames(kappamat) <- rownames(kappamat) <- c("Get stressed out easily",
                                              "Am relaxed most of the time",
                                              "Worry about things",
                                              "Seldom feel blue",
                                              "Am easily disturbed",
                                              "Get upset easily",
                                              "Change my mood a lot",
                                              "Have frequent mood swings",
                                              "Get irritated easily",
                                              "Often feel blue")

pmat <- matrix(nrow = dim(emotdat2)[2],
                   ncol = dim(emotdat2)[2])

for(i in 1:dim(emotdat2)[2]){
  for(j in 1:dim(emotdat2)[2]){
    pmat[i,j] <- kappa2(emotdat2[,c(i,j)], weight = "squared")$p.value
  }
}

diag(pmat) <- 0

col <- colorRampPalette(rev(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA")))
corrplot(kappamat, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=90, #Text label color and rotation
         # Combine with significance
         #p.mat = pmat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE, 
         cl.pos = "n",
         tl.cex = .75,
         number.cex = .75
)
```

##Cronbachs alpha

```{r}
emot.alpha <- psych::alpha(emotdat2, n.iter = 10000)
```


# Investigating Conscientiousness

```{r}
condat <- questdat[,c(1,4,9,14,19,24,29,34,39,44,49)]

#recoding word responses to numeric responses
condat[,-1] <- apply(condat[,-1], 2, function(x){ifelse(x=="Very Accurate", 5, 
                                           ifelse(x=="Moderately Accurate", 4,
                                                  ifelse(x=="Neither Accurate nor Inaccurate", 3, 
                                                         ifelse(x=="Moderately Inaccurate", 2,
                                                               ifelse(x=="Very Inaccurate", 1, NA)))))})

#reverse code negative questions
condat[,c(3,5,7,9)] <- apply(condat[,c(3,5,7,9)], 2, function(x){ifelse(x==1, 5, 
                                           ifelse(x==2, 4,
                                                  ifelse(x==3, 3, 
                                                         ifelse(x==4, 2,
                                                               ifelse(x==5, 1, NA)))))})

condat <- condat[which(condat$Record.ID %in% big5data_final$Id),]

condat$Gender <- big5data_final$Gender[which(big5data_final$Id %in% condat$Record.ID)]

```


###kappa

```{r}
condat2 <- condat[,-c(1,12)]

M <- cor(condat2, method = "spearman")
#corrplot(M, type="upper")

kappamat <- matrix(nrow = dim(condat2)[2],
                   ncol = dim(condat2)[2])

for(i in 1:dim(condat2)[2]){
  for(j in 1:dim(condat2)[2]){
    kappamat[i,j] <- kappa2(condat2[,c(i,j)], weight = "squared")$value
  }
}

colnames(kappamat) <- rownames(kappamat) <- c("Get stressed out easily",
                                              "Am relaxed most of the time",
                                              "Worry about things",
                                              "Seldom feel blue",
                                              "Am easily disturbed",
                                              "Get upset easily",
                                              "Change my mood a lot",
                                              "Have frequent mood swings",
                                              "Get irritated easily",
                                              "Often feel blue")

pmat <- matrix(nrow = dim(condat2)[2],
                   ncol = dim(condat2)[2])

for(i in 1:dim(condat2)[2]){
  for(j in 1:dim(condat2)[2]){
    pmat[i,j] <- kappa2(condat2[,c(i,j)], weight = "squared")$p.value
  }
}

diag(pmat) <- 0

col <- colorRampPalette(rev(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA")))
corrplot(kappamat, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=90, #Text label color and rotation
         # Combine with significance
         #p.mat = pmat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE, 
         cl.pos = "n",
         tl.cex = .75,
         number.cex = .75
)
```

##Cronbachs alpha

```{r}
con.alpha <- psych::alpha(condat2, n.iter = 10000)
```


# Investigating Extraversion

```{r}
extradat <- questdat[,c(1,2,7,12,17,22,27,32,37,42,47)]

#recoding word responses to numeric responses
extradat[,-1] <- apply(extradat[,-1], 2, function(x){ifelse(x=="Very Accurate", 5, 
                                           ifelse(x=="Moderately Accurate", 4,
                                                  ifelse(x=="Neither Accurate nor Inaccurate", 3, 
                                                         ifelse(x=="Moderately Inaccurate", 2,
                                                               ifelse(x=="Very Inaccurate", 1, NA)))))})

#reverse code negative questions
extradat[,c(3,5,7,9,11)] <- apply(extradat[,c(3,5,7,9,11)], 2, function(x){ifelse(x==1, 5, 
                                           ifelse(x==2, 4,
                                                  ifelse(x==3, 3, 
                                                         ifelse(x==4, 2,
                                                               ifelse(x==5, 1, NA)))))})

extradat <- extradat[which(extradat$Record.ID %in% big5data_final$Id),]

extradat$Gender <- big5data_final$Gender[which(big5data_final$Id %in% extradat$Record.ID)]

```

##kappa

```{r}
extradat2 <- extradat[,-c(1,12)]

M <- cor(extradat2, method = "spearman")
#corrplot(M, type="upper")

kappamat <- matrix(nrow = dim(extradat2)[2],
                   ncol = dim(extradat2)[2])

for(i in 1:dim(extradat2)[2]){
  for(j in 1:dim(extradat2)[2]){
    kappamat[i,j] <- kappa2(extradat2[,c(i,j)], weight = "squared")$value
  }
}

colnames(kappamat) <- rownames(kappamat) <- c("Am the life of the party",
                                              "Don't talk a lot",
                                              "Feel comfortable around people",
                                              "Keep in the backgroud",
                                              "Start conversations",
                                              "Have little to say",
                                              "Talk to a lot of different people at parties",
                                              "Don't like to draw attention to myself",
                                              "Don't mind being the center of attention",
                                              "Am quiet around strangers")

pmat <- matrix(nrow = dim(extradat2)[2],
                   ncol = dim(extradat2)[2])

for(i in 1:dim(extradat2)[2]){
  for(j in 1:dim(extradat2)[2]){
    pmat[i,j] <- kappa2(extradat2[,c(i,j)], weight = "squared")$p.value
  }
}

diag(pmat) <- 0

col <- colorRampPalette(rev(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA")))
corrplot(kappamat, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=90, #Text label color and rotation
         # Combine with significance
         #p.mat = pmat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE, 
         cl.pos = "n",
         tl.cex = .75,
         number.cex = .75
)
```

##Cronbachs alpha

```{r}
extra.alpha <- psych::alpha(extradat2, n.iter = 10000)
```


# Investigating Openness to Experience

```{r}
opendat <- questdat[,c(1,6,11,16,21,26,31,36,41,46,51)]

#recoding word responses to numeric responses
opendat[,-1] <- apply(opendat[,-1], 2, function(x){ifelse(x=="Very Accurate", 5, 
                                           ifelse(x=="Moderately Accurate", 4,
                                                  ifelse(x=="Neither Accurate nor Inaccurate", 3, 
                                                         ifelse(x=="Moderately Inaccurate", 2,
                                                               ifelse(x=="Very Inaccurate", 1, NA)))))})

#reverse code negative questions
opendat[,c(3,5,7)] <- apply(opendat[,c(3,5,7)], 2, function(x){ifelse(x==1, 5, 
                                           ifelse(x==2, 4,
                                                  ifelse(x==3, 3, 
                                                         ifelse(x==4, 2,
                                                               ifelse(x==5, 1, NA)))))})

opendat <- opendat[which(opendat$Record.ID %in% big5data_final$Id),]

opendat$Gender <- big5data_final$Gender[which(big5data_final$Id %in% opendat$Record.ID)]

```


##kappa

```{r}
opendat2 <- opendat[,-c(1,12)]

M <- cor(opendat2, method = "spearman")
#corrplot(M, type="upper")

kappamat <- matrix(nrow = dim(opendat2)[2],
                   ncol = dim(opendat2)[2])

for(i in 1:dim(opendat2)[2]){
  for(j in 1:dim(opendat2)[2]){
    kappamat[i,j] <- kappa2(opendat2[,c(i,j)], weight = "squared")$value
  }
}

colnames(kappamat) <- rownames(kappamat) <- c("Have a rich vocabulary",
                                              "Have difficulty understanding abstract ideas",
                                              "Have a vivid imagination",
                                              "Am not interested in abstract ideas",
                                              "Have excellent ideas",
                                              "Do not have a good imagination",
                                              "Am quick to understand things",
                                              "Use difficult words",
                                              "Spend time reflecting on things",
                                              "Am full of ideas")

pmat <- matrix(nrow = dim(opendat2)[2],
                   ncol = dim(opendat2)[2])

for(i in 1:dim(opendat2)[2]){
  for(j in 1:dim(opendat2)[2]){
    pmat[i,j] <- kappa2(opendat2[,c(i,j)], weight = "squared")$p.value
  }
}

diag(pmat) <- 0

col <- colorRampPalette(rev(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA")))
corrplot(kappamat, method="color", col=col(200),  
         type="upper", order="hclust", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=90, #Text label color and rotation
         # Combine with significance
         #p.mat = pmat, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag=FALSE, 
         cl.pos = "n",
         tl.cex = .75,
         number.cex = .75
)
```

##Cronbachs alpha

```{r}
open.alpha <- psych::alpha(opendat2, n.iter = 10000)
```

